\Large{Holier Than Thou: Partisan Gap in Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}

### 2022-12-16 ms/adult.tex
revise ms
Update ms

\begin{figure}[h]
\centering
\caption{Distribution of Consumption of Pornography Online}
\includegraphics[scale=.75]{figs/distribution_duration_on_adultsites.pdf}
\label{fig:distribution_duration}
\end{figure}

\begin{figure}[h]
\centering
\caption{Proportion of Visits to Pornographic Sites}
\includegraphics[scale=.75]{figs/distribution_proportion_adultsites_duration.pdf}
\label{fig:distribution_prop_duration}
\end{figure}

\begin{figure}[h]
\centering
\caption{Distribution of Consumption of Pornography Online by Party}
\includegraphics[scale=.75]{figs/distribution_duration_on_adultsites_by_party.pdf}
\label{fig:distribution_duration}
\end{figure}

@@

\input{tabs/models.tex}

@@

\clearpage
\section{Consequence of Using Alternate Ways of Measuring Pornography}
\subsection{Keyword Classifier}
Our first classifier is based on just the domain name and domain suffix. In particular, we use a calibrated keyword classifier. The features of the model are whether any of the following keywords are present in the domain name:

@@

\begin{figure}[h]
\centering
\caption{Distribution of Consumption of Pornography Online}
\includegraphics[scale=.75]{figs/distribution_proportion_adultsites_visits.pdf}
\label{fig:distribution_visits}
\end{figure}

\begin{figure}[h]
\centering
\caption{Proportion of Visits to Pornographic Sites}
\includegraphics[scale=.75]{figs/distribution_proportion_adultsites_visits_by_party.pdf}
\label{fig:distribution_prop_visits}
\end{figure}

\begin{figure}[h]
\centering
\caption{Distribution of Consumption of Pornography Online by Party}
\includegraphics[scale=.75]{figs/distribution_visits_to_adultsites_by_party.pdf}
\label{fig:distribution_visits_party}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\caption{Distribution of Consumption of Pornography Online}
\includegraphics[width=.55\linewidth]{../figs/distribution_duration_on_adultsites.pdf}
\caption*{\footnotesize \emph{Notes:} 
	Hours spent on adult sites by individuals who consumed pornography in the sample period.
	Individuals are split into deciles with each bin containing approximately the same number of individuals.
	Height of bars indicate mean of each bin.
	Capped vertical bars are 95\% confidence intervals.
	See \cref{tab:distribution_duration} for the more tabulated values.
}
\label{fig:distribution_duration}
\end{figure}

\begin{figure}[h]
\centering
\caption{Proportion of Visits to Pornographic Sites}
\includegraphics[scale=.75]{../figs/distribution_proportion_duration_on_adultsites.pdf}
\label{fig:distribution_prop_duration}
\end{figure}

\begin{figure}[h]
\centering
\caption{Distribution of Consumption of Pornography Online by Party}
\includegraphics[scale=.75]{../figs/distribution_duration_on_adultsites_by_party.pdf}
\label{fig:distribution_duration_party}
\end{figure}

To formally test for these differences, we ran quantile regression, regressing the duration on party.

\begin{figure}[h]
\centering
\caption{Distribution of Consumption of Pornography Online by Party}
\includegraphics[scale=.75]{../figs/quantile_reg_nonzero_duration_adult.pdf}
\label{fig:quantile_regression_duration}
\end{figure}

@@

\input{../tabs/models.tex}

@@

\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
	\caption{Distribution of Consumption of Pornography Online}
	\label{tab:distribution_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}cc@{\hspace{0\tabcolsep}}}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		See \cref{fig:distribution_duration} for the plot.
	}
\end{table}

\clearpage
\section{Top 25 Adult Domains}

\begin{figure}[h]
\centering
\caption{Proportion of Visits to Pornographic Sites}
\includegraphics[scale=.75]{../figs/top_25_adultsites.pdf}
\label{fig:top25}
\end{figure}

\section{Consequence of Using Alternate Ways of Measuring Pornography}
\subsection{Keyword Classifier}
Our first classifier is based on just the domain name and domain suffix. In particular, we use a calibrated keyword classifier. The features of the model are whether any of the following keywords are present in the domain name:

@@

\begin{figure}[h]
\centering
\caption{Distribution of Consumption of Pornography Online}
\includegraphics[scale=.75]{../figs/distribution_proportion_adultsites_visits.pdf}
\label{fig:distribution_visits}
\end{figure}

\begin{figure}[h]
\centering
\caption{Proportion of Visits to Pornographic Sites}
\includegraphics[scale=.75]{../figs/distribution_proportion_adultsites_visits_by_party.pdf}
\label{fig:distribution_prop_visits}
\end{figure}

\begin{figure}[h]
\centering
\caption{Distribution of Consumption of Pornography Online by Party}
\includegraphics[scale=.75]{../figs/distribution_visits_to_adultsites_by_party.pdf}
\label{fig:distribution_visits_party}
\end{figure}
